%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}
\hypersetup{%
    pdfborder = {0 0 0}
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Hitesh}{Santwani}{ % Your name profile or other web address
\href{https://hiteshsantwani.github.io}{\bf https://hiteshsantwani.github.io} \\
\href{mailto:hiteshka@buffalo.edu}{hiteshka@buffalo.edu} | 716.603.0959 | Buffalo, NY% Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}
Java and Spring MVC \\
Python and iPython Notebook \\
SQL and R\\

\sectionspace % Some white space after the section

\subsection{Data Science}
Regression \\
Classification \\
Support Vector Machines \\
Naive Bayes \\
K-Nearest Neighbors \\
Decision Trees \\
Cluster Analyses \\
Deep Learning \\

\sectionspace % Some white space after the section

\subsection{Software}
Amazon Web Services \\
Spark and Hadoop \\
Git and Github \\

\sectionspace % Some white space after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Big Data Specialization}

\descript{University of California San Diego}
\location{Expected January 2019 | Online}

\sectionspace % Some white space after the section

\subsection{MS, Data Science}
\descript{University at Buffalo}
\location{August 2018 - present | Buffalo, NY \\ Course Work Includes in depth Knowledge and skills in Data Engineering and exhaustive study of Machine Learning along with Essential EDA skills. }

\sectionspace % Some white space after the section

%------------------------------------------------

\subsection{B.E, Information Technology}
\descript{University of Mumbai}
\location{June 2015 | Mumbai, India \\
Graduated with First Class}

\sectionspace % Some white space after the section


%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/hiteshsantwani}{\bf hiteshSantwani} \\
LinkedIn:// \href{https://www.linkedin.com/in/hiteshsantwani/}{\bf hiteshSantwani} \\
Hackerrank:// \href{https://www.hackerrank.com/hiteshsantwani35}{\bf hiteshSantwani} \\

\sectionspace % Some white space after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Accenture Solutions Pvt. Ltd}
\descript{| Mumbai, India \\ Software Engineer (June 2017 - July 2018) \\ Associate Software Engineer (October 2015 to May 2017)}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Application Developer for the client (A major North American Corporate \& Investment Bank).
\item Implemented Application modularization using spring boot for the migration of platform responsible for trading high volume of over the counter derivatives to hybrid cloud.
\item Achieved reduction in technical debt and increased velocity of application development by 50\%.
\item Developed new features to chase the institutional clients for trade affirmation and Accomplished target of 1.3 times Order Fill Rate.
\item Languages used: Java, java script, XQuery. Frameworks: Spring MVC, Hibernate.
\end{tightitemize}


\sectionspace % Some white space after the section

\section{Professional Certifications}

\runsubsection{AWS Certified Solutions Architect Associate} \\
\location{May 2018 - May 2020 | Mumbai, India}

\runsubsection{AWS Certified Developer Associate} \\
\location{December 2017 - December 2019 | Mumbai, India}

\sectionspace % Some white space after the section

\section{Relevant Projects}

\runsubsection{Big Data - Capstone Project}
\descript{| UNIVERSITY OF CALIFORNIA SAN DIEGO }
\location{October 2018 - January 2019 | Online}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item A big data ecosystem using tools and methods form the earlier courses in this specialization. Analyze a data set simulating big data generated from a large number of users who are playing an imaginary game “Catch the Pink Flamingo”. \\ Tools Used: Splunk, KNIME, Spark's MLLib, Gephi and Open Office, Jupyter notebook.

\end{tightitemize}

\sectionspace % Some white space after the section

\runsubsection{PyTorch Scholarship Challenge from Facebook (Flower Classifier)}
\descript{| UDACITY }
\location{November 2018 - January 2019 | Online}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Deep learning model for predicting the species of the flower from the picture of the flower. Achieved 95\% Accuracy (\href{https://colab.research.google.com/github/hiteshsantwani/QPA/blob/master/Facebook_DeepLearningChallenge.ipynb}{\bf Click Here for demo}).\\ Skills: Deep Learning, Python, PyTorch.
\end{tightitemize}

\sectionspace % Some white space after the section

\runsubsection{Running a successful country RSC – 101}
\descript{| MS, Data Science }
\location{November 2018 - December 2018 | Buffalo, NY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item (\href{https://github.com/ubdsgroup/eas503projects/blob/master/Project2018/Group\%2015/Final\%20Report.pdf}{\bf Click Here for demo}) Exploratory Data Analysis and Data cleansing on Two major data sets (Gapminder and world bank) to uncover the factors that contributed in development of the emerging economies in the last 40 years. \\ Skills: Jupyter notebook, Plotly Dashboard, SQLite, Matplotlib, Ipython Widgets, Pandas.

\end{tightitemize}

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}